A Partitioning Algorithm for \\ Maximum Common Subgraph Problems

### 2017-08-23 talk/talk.tex
Think I want this slide
I'm plotting a better talk

    \begin{itemize}
        \item Unlabelled variant: 4,100 instances from a
          database of randomly-generated maximum common subgraph instances (up~to 50 vertices)
        \item Labelled variant: 8,140 instances from the same database (up~to 100 vertices)
        \item We also ran the algorithms on a set of 5,725 larger instances (up~to 6,671 vertices)
    \end{itemize}

@@

@@

>>>>

    \begin{itemize}
        \item Unlabelled variant: 4,100 instances from a
          database of randomly-generated maximum common subgraph instances (up~to 50 vertices)
        \item Labelled variant: 8,140 instances from the same database (up~to 100 vertices)
        \item We also ran the algorithms on a set of 5,725 larger instances (up~to 6,671 vertices,
            one graph is often smaller than the other)
    \end{itemize}

@@

\begin{nearlyplainframe}[t]{}
    \centering
        \input{gen-graph-plain-james-versus-cp-fc-runtimes-scatter}
\end{nearlyplainframe}

@@

\begin{nearlyplainframe}[t]{}
    \centering
        \input{gen-graph-sip-james-versus-kdown-nodes-scatter}
\end{nearlyplainframe}
